DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
modification cosmo table

\begin{abstract}

@@

Nevetheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
\todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}. This can probably be overcome by considering a specific class of functions, such as bandlimited function.
Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix \ref{sec: appendix: proof of theorem}.

@@

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal. The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ \citep{gorski1999healpixprimer}.

@@

\begin{table}
    \centering
    \begin{tabular}{l c c c}
		\toprule
		& accuracy & conv. equiv. error & NN inv. error \\
		\midrule
		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{can we?} \\
		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} \\
		8 neighbors, optimal kernel width $\hat{t} = ??$ & 87.1 & \todo{??} \\
		20 neighbors, optimal kernel width $\hat{t} = ??$ & 91.25 & \todo{??} \\
		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
		\bottomrule
    \end{tabular}
	\caption{
		Results on the classification of partial convergence maps.
		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
		\todo{add speed to show trade-off}
	}
    \label{tab:cosmo}
\end{table}

>>>>

\begin{abstract}
Selecting the right convolution for a spherical neural network is a delicate trade-off between its efficiency and its exactictude with respect of equivariance. DeepSphere, as a graph based method strikes as a controllable balance between these two aspect. This contribution study how the construction of its underlying graph both theoretically and empirically.

@@

Nevetheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
% \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}[Sec 3], but does for a class of Lipschitz functions \cite{belkin2005towards}[Sec 6]. 
\todo{Update once discussed with Martino}
Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix \ref{sec: appendix: proof of theorem}.

@@

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error \eqref{eq:mean equivariance error} by generating $N$ monochromatic signals and $M$ random rotations for each signal. 
The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ \citep{gorski1999healpixprimer}.

@@

\begin{table}
    \centering
    \begin{tabular}{l c c c c}
		\toprule
		& accuracy & conv. equiv. error & inference \\ % & training time & NN inv. error
		\midrule
		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} &  \\ % &  & \todo{can we?}
		8 neighbors, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} &  \\
		8 neighbors, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} & 187\,ms \\ % & 1\,h\,45\,m
		8 neighbors, optimal kernel width & 87.1 & \todo{??} & 185\,ms \\ % & 1\,h\,45\,m
		20 neighbors, optimal kernel width & 91.3 & \todo{??} & 250\,ms \\ % & 2\,h\,30\,m
		40 neighbors, optimal kernel width & 92.5 & \todo{??} & 363\,ms\\ % & 3\,h\,45\,m
		\bottomrule
    \end{tabular}
	\caption{
		Results on the classification of partial convergence maps.
		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
		\todo{add speed to show trade-off}
	}
    \label{tab:cosmo}
\end{table}
